---
title: "R Markdown and Leaflet - 2017 Car crash data in Allegheny County"
author: "Omer Shechter"
date: "23 November 2018"
output: html_document
---
# Project Summary
This project is the Week 2 assignment of the data product coursera course.
The project illustrates the work with Maps using leaflet, and the use of R markdown.
The data set is the car crash data for the year 2017 in Allegheny County.
The data set is taken from this link :
https://data.wprdc.org/dataset/allegheny-county-crash-data/resource/bf8b3c7e-8d60-40df-9134-21606a451c1a.

The Interactive map illustrates : 
Creating a basic map. 
Adding multiple markers (marking the car crash location).
Using customize icon to the markers.
Using clusters.
Using popup : 
The popup presents : 
  The number of cars involves in the crash.
  The number of deaths (Fatalities ).
  The number of people who suspected as a drunk driver. 
  The number of people who suspected in drugs use. 
  The Map uses a control option to select and show the car accidents per specific month 
```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries.
```{r}
library(leaflet)
library(tidyr)
library(dplyr)
```


Read 2017 Car crash data in Allegheny County.
Data is loaded from :
https://data.wprdc.org/datastore/dump/bf8b3c7e-8d60-40df-9134-21606a451c1a
```{r}
DF<-read.csv("CarCrash2017.csv")

```
# Interactive MAP - Total car crash by month.

Subset the location of the car crash 
Keep the data about the month of the accident.
Create a new column with the month's names instead of a number. 
Since there is a large number of the crash 
There will be an option to show car crash per specific month
For information to present in a popup :
AUTOMOBILE_COUNT -  the number of cars involved 
DRINKING_DRIVER - Alcohol involved? 
FATAL_COUNT - Total number of death 
ILLEGAL_DRUG_RELATED - Ilegal drug involvement 
```{r}
dfCrash<-select(DF,DEC_LAT,DEC_LONG,CRASH_MONTH,AUTOMOBILE_COUNT,DRINKING_DRIVER,FATAL_COUNT,ILLEGAL_DRUG_RELATED)
colnames(dfCrash)<-c("latitude","longitude","Month Crash","No.Cars.Involved","Drinking.Driver","Death.Count","Drug.Involved")
dfCrash<-dfCrash %>% drop_na()
dfCrash<-mutate(dfCrash,Month.Crash.Name=month.name[dfCrash$`Month Crash`])
```

Use a PNG file as an icon for markers on the MAP.
```{r}
CarsIcon <- makeIcon("CarsIcon1.png",iconWidth = 45, iconHeight = 45)
```

Helper function to add markers.
```{r}
####################################
# Add_Marker --- Helper function   #
#Paramters : 
#my_map - leaflet object - markeers will be added to this object 
#lat_ln_data - Data frame with the lat and long (of the required markers 
#groupname - The group name of the markers
#popup - Popup content 
#IconMarker - The icon of the marker

Add_Marker <- function(my_map,lat_ln_data,groupname,content,iconMarker=CarsIcon) {
#Add markers which allow creating multiple markers, with ICON and with popup
#The cluster option is selected 
  addMarkers(my_map,data=lat_ln_data,clusterOptions = markerClusterOptions(),group =groupname,icon = iconMarker,popup = paste("Car involved:", content$No.Cars.Involved ,"<br>",
             "Fatality:",content$Death.Count,"<br>",
              "Drugs Involved :", content$Drug.Involved,"<br>",
               " Alcohol involved:",content$Drinking.Driver))
  #addPopups(my_map, lat_ln_data$latitude,lat_ln_data$longitude,content)
  
}

```

# 2017 Car crash data of Allegheny County
Create the Interactive MAP using leaflet 
```{r echo=FALSE ,message = FALSE,fig.width=11,fig.height=11}
Alat<-c(40.675986,40.663033,40.226055,40.198162,40.233168,40.476416 )
Alng<-c(-80.147219, -79.703291,-79.799402,-79.883659, -79.971751,-80.355053)


my_map<-dfCrash %>% 
  leaflet() %>%
  addTiles() 
#Create for loop to create 12 groups one for each month 
# The groups are needed to support interactive control layer 
# which allow the user to select the month 
for (index in 1:12){
  my_map<-Add_Marker(my_map,subset(dfCrash,dfCrash$`Month Crash`==index),month.name[index],subset(dfCrash[,c("No.Cars.Involved","Drinking.Driver","Death.Count","Drug.Involved")],dfCrash$`Month Crash`==1))
  
}

addPolygons(my_map,lng = Alng,lat = Alat,weight = 5,fillOpacity = 0.05,group = "County")%>%
  #Layers control
  addLayersControl(baseGroups = month.name,overlayGroups =  "County",
    options = layersControlOptions(collapsed = FALSE)
  )
  
```



